Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-12 R0V0.tex
Item 25 (cont.): small change
Item 26. Start to implement the example.

\mypara Inequality~\eqref{eq:Artstein-Sontag:inequality} is satisfied, whenever the matrix inequality
\begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
 	\ker(B)^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)\ker(B)\prec0
\end{equation} 
holds, where $\ker(B)$ is a full-rank matrix satisfying $B^\top\ker(B)\equiv0$.

@@

\mypara A case where structured controller design is relevant is on distributed design for network systems. Let $N>0$ be a constant integer, consider the graph describing the network structure in Figure~\ref{fig:graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/GraphStructure.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}
For each index $i\in\mathbb{N}_{[1,N]}$, the agents dynamics is described by the system
\begin{equation}\tag{\ref{eq:example}}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i,
	\end{array}\right.$}
\end{equation}
where for convenience $x_0=x_1$ and $x_N=x_{N+1}$.

@@

\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.

>>>>

\mypara Condition~\eqref{eq:Arstein-Sontag} is satisfied, whenever the matrix inequality
\begin{equation}\label{eq:Artstein-Sontag:inequality:dual}
 	\ker(B)^\top\left(-\dot{W}+AW + WA^\top+2\lambda W\right)\ker(B)\prec0
\end{equation} 
holds, where $\ker(B)$ is a full-rank matrix satisfying $B^\top\ker(B)\equiv0$.

@@

\mypara A case where structured controller design is relevant is on distributed design for network systems. For a given integer $N>0$, consider the system that describes the dynamics of each agent
\begin{equation}\tag{\ref{eq:example}}
	\scalebox{0.95}{$\left\{\begin{array}{rcl}
		\dot{x}_i&=&-x_i-x_i^3+y_i^2 + 0.01\left(x_{i-1}^3 - 2x_i^3 +x_{i+1}^3\right)\\
		\dot{y}_i&=&u_i\;,
	\end{array}\right.$}
\end{equation}
where $i\in\mathbb{N}_{[1,N]}$ and for convenience $x_0=x_1$ and $x_N=x_{N+1}$.

@@

\mypara In the remained of this section, two network topologies are considered to illustrate the results presented in this paper. The numerical results were obtained employing the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b

\subsection{Circumference topology}

\mypara The graph describing the network structure in provided in Figure~\ref{fig:cycle graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/CyclicGraph.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:cycle graph}
\end{figure}

\subsection{Chain topology}

\mypara The graph describing the network structure in provided in Figure~\ref{fig:graph}.
\begin{figure}[htpb!]
	\centering
	\input{./imgs/GraphStructure.pdf_tex}
	\caption{Graph describing the network composed of systems of the form \eqref{eq:example}.}
	\label{fig:graph}
\end{figure}

\mypara The matrix $W$ obtained is given by $\mathbin{\mathtt{diag}}(\overline{W},\overline{W},\overline{W},\overline{W})$, where $\overline{W}=\mathbin{\mathtt{diag}}(0.72,0.19)$. The matrix $Y$ is given by
\begin{equation*}
	Y(q)=\begin{bmatrix}
		\underline{Y}(q_1,\breve{q}_1)&\overline{Y}(q_1,\breve{q}_1)&0_{2\times1}&\overline{Y}(q_1,\breve{q}_1)\\
		\overline{Y}(q_2,\breve{q}_2)&\underline{Y}(q_2,\breve{q}_2)&\overline{Y}(q_2,\breve{q}_2)&0_{2\times1}\\
		0_{2\times1}&\overline{Y}(q_3,\breve{q}_3)&\underline{Y}(q_3,\breve{q}_3)&\overline{Y}(q_3,\breve{q}_3)\\
		\overline{Y}(q_4,\breve{q}_4)&0_{2\times1}&\overline{Y}(q_4,\breve{q}_4)&\underline{Y}(q_4,\breve{q}_4)
	\end{bmatrix}\;,
\end{equation*}
where $\underline{Y}(q_i,\breve{q}_i)=-2.26\begin{bmatrix}y_i,&y_i^2+x_i^2+\sum_{j\in\mathscr{N}(i)}y_j^2+x_j^2\end{bmatrix}$,
$\overline{Y}(q_i,\breve{q}_i)=\begin{bmatrix}0.002y_i,0\end{bmatrix}$ and $0_{2\times1}$ stands for the vector $[0,0]\in\mathbb{R}^2$.

\mypara When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
n\dfrac{n+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
monomials to be computed. This motivates the approach proposed in this paper.
